### 2019-03-17 README.Rmd
Add comment about raw data source
Pass goodpractice except for covr, set up CI

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)

@@

>>>>

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![CircleCI](https://circleci.com/gh/ecohealthalliance/citesdb.svg?style=svg){data-external="1"}](https://circleci.com/gh/ecohealthalliance/citesdb)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)

@@

If you don't need any of the bells and whistles of this package, you can download
the raw data as a single compressed TSV from the [releases page](https://github.com/ecohealthalliance/citesdb/releases),
or as a `.zip` file of many CSV files from original source at <https://trade.cites.org/>.
